### 2016-08-17 Theorem1_FP.tex
Proof1 new syntax

%\acnote{I am moving comments to end of the proof in tex file and commenting them as the labels are getting mangled}
\heading{Linear-PRF construction. }
Here we consider a hash-based filter that was attacked by Neidermayer et al. in~\cite{xxx}.  Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be defined as follows.  Fix non-empty sets ~$\univ$, $\calK$ and integers $k,m,n>0$.  Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.  The $\Hash$ algorithm samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.  The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones. The following result shows, informally, that if~$F$ is a good PRF and the (non-adaptive) FP rate is sufficiently small, then $B_\mathrm{lin}$ is secure against adaptive FP-finding adversaries.

\begin{theorem}\label{thm1}
Fix $k,m,n,r>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
For any adversary~$A$ that makes a total of~$q$ queries to its oracle
and has time-complexity~$O(t)$,
there exist adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
\end{theorem}
Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, non-adaptive) FP-probability for~$B_\mathrm{lin}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as 
$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
trying to find a single FP in each of~$r$ independent``rounds'', each round
consisting of~$q$ attempts.

\begin{proof}[\Cref{thm1}]
The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpFPSecHash{B_\mathrm{lin},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,

\begin{equation}
\AdvFPSecHash{B_{\mathrm{lin}},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
\end{equation}

@@

\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(S, \pubaux)$\\
When $A$ asks $\TestOracle(q)$:\\
\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
\nudge if $a \neq q(S)$ then \\
\nudge \nudge $\err \gets \err +1$\\
Return~$(a,\err )$
When $A$ halts: \\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(S, \pubaux)$\\
When $A$ asks $\TestOracle(q)$:\\
\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
\nudge if $a \neq q(S)$ then \\
\nudge \nudge $\err \gets\err +1$\\
Return~$(a,\err )$
When $A$ halts: \\
if $\err  < r$ then Return 0\\
Return 1\\\\
\oracle{$\HashOracle(x)$}\\
$a \getsr [m]$\\
if $T[x] \neq \undefined$\\
\nudge $a \gets T[x]$\\
$T[x] \gets a$\\
Ret  $\calO(x) + i\cdot a$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

@@

Recall that adversary~$A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive.  We can also assume that every point in $\calZ$ has already been queried to $\QryOracle$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
Under these assumptions, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in \Cref{fig:D}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be the false positives; it simulates the~$\QryOracle$ by returning 1 on the guessed queries, and 0 otherwise; and it halts by outputting the set of guessed queries.  Thus we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1}$.

Note that $\tilde{B}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).  Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a non-adaptive adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.  For $r>1$, we observe that~$A$'s queries are distinct and not elements of the original set~$S$, since we assume no pointless queries. Hence, so are the points $x_1,x_2,\ldots,x_r$ returned by~$D$.  Let $\calF_i$ be the event that~$x_i$ is a false positive.  Since $\game{4}$ (equivalently $\tilde{B}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent. 
\[
\Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
\]

To summarize, we have 
\[
\AdvFPSecHash{B_{\mathrm{lin}},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. \hfill \qed

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
$c\gets 0$, $\bad \gets \false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $c \in \mathcal{I}$ and $a \neq q(S)$ then \\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $a \neq q(S)$ then \\
\nudge $\bad \gets \true$\\
\nudge $\err \gets\err +1$\\
Return~$(v,\err )$
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

@@

%\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\begin{figure}
\centering
\fpage{0.35}
{
$\adversaryv{D(S)}$\\[4pt]
$c \gets 0$, $\calX \gets \emptyset$\\
$\err \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
Run $A(S)$\\
When $A$ asks $\QryOracle(x)$:\\
\nudge $c \gets c+1$\\
\nudge $r \gets 0$\\
\nudge if $c \in \mathcal{I}$\\
\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
\nudge \nudge $r \gets 1$\\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Ret $(r,\err )$\\
When $A$ halts:\\
\nudge Ret $\calX$
}
\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\end{figure}

\iffalse
%Comments
\tsnote{I'll need to rewrite all below here.  The current text is too hand-wavy and fast.}
\tsnote{`In transitioning from $\game{2}$ to $\game{3}$ we
  replace the all-at-once sampling of random functions~$\rho_1,\rho_2$
with lazying sampling in the $\HashOracle$, which is the only place
these random functions are used.  This does not alter the input-output
behavior of the $\HashOracle$.''  Why do we do this?}
We also sample $r$~distinct random integers are chosen \tsnote{why?
  What are we setting up?} and the $\QryOracle$ oracle sets a $\bad$
flag if query response for any of the $r$ queries is false or any of
the $q-r$ queries return true. \tsnote{We
  set $\bad$ to $\true$ if the queries indexed by the
  set~$\mathcal{I}$ fail to be false-positives, or if any of the
  remaining queries \emph{are} false-positives.  Again, why are we
  doing this?  }
\tsnote{How does the last line follow from the games?  I mean, it
  isn't obvious to me that your $\game{5}$ is equivalent to $\game{4}$.  The
  latter looks at the adversary's output~$\mathcal{Z}$, but the former
ignores this and looks at this new set~$\mathcal{Y}$.  Why are these
equivalent with respect to the events $\game{4}(A)=1$ and
$\game{5}(A)=1$?  Just looking at the $\QryOracle$ in the two games,
it appears that they have pretty different behaviors. I mean, in
$\game{4}$ the oracle still returns what it is supposed to, even if
$\bad\gets\true$.  But in $\game{5}$ the oracle returns fixed values,
no matter if the query is or is not a FP.  You have to explain why
these changes are okay.  Also, why is this new set~$\mathcal{Y}$
necessary?  }
\tsnote{The point that needs to be made about the relationship between
  $\game{4}$ and $\game{5}$ is this.  $\game{4}$ returns 1 only if
  $\bad=\false$ at the end of the game.  In turn, this implies that
  the game managed to ``guess'', prior to the execution of~$A$, which
  of its queries would result in false-positives.  (By the way, we
  need to state an assumption here: that~$A$ halts and
  outputs~$\mathcal{Z}$ (of size~$r$) as soon as its queries
  reveal~$r$ false positives.  This is without loss of generality; say
why.  I guess you also need to assume that every point in
the~$\mathcal{Z}$ output by~$A$ has already been queried
to~$\QryOracle$.  Strictly speaking this is not without loss of
generality, but would be easily enforced (in the original
  security definitions) by counting as part of the number of
  queries~$q$ the points in~$\mathcal{Z}$.  Without these assumptions,
things don't quite work.)  Hence, if $\game{4}(A)=1$ there is a
non-adaptive adversary~$D$ that finds~$r$ false positives against
$\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but
with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$,
respectively.  (Note, this is \emph{not} the adversary~$D$ that you
give, because the one you give simulates things that it would be given
in the FP game, e.g. the set~$S$.)  That is, $\Prob{\game{4}(A)=1} =
\AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D}$.  (So I guess there's no
need for $\game{5}$.)  Now argue that this advantage is upperbounded
	by what the theorem claims, i.e. the KM bound raised to~$r$.}

In $\game{3}(A)$, the hash functions are linear combinations of two random points
in $[m]$, similar to $\game{2}(A)$.

So, both have equal probability of returning 1.  \tsnote{``The value
  of~$\bad$ does not affect the value returned by~$\game{3}$. Thus we
  conclude that...'' }
\begin{equation}
\Prob{\game{2}(A)=1} = \Prob{\game{3}(A)=1}\label{eq:3}
\end{equation}

The probability of winning  $\game{3}(A)$ is same as $\game{4}(A)$,
except $\game{4}(A)$ outputs 0 if $\bad$ flag is
set.\tsnote{I don't understand this sentence.  What you mean to say is
  something like this: ``By construction, $\game{3}$ and $\game{4}$
  are identical-until-bad.  In addition, $\game{4}$ returning 1
  implies that $\bad$ is never set to~$\true$.  From these two
  observations, we can conclude that $\Prob{\game{4}(A)=1} =
  \Prob{\game{3}(A)=1 \wedge \neg\bad}$.'' }
In short, $\game{3}(A)$ and $\game{4}(A)$ are identical untill $\bad
=true$.  On the  other hand, $\game{5}(A)$ simulates the non-adaptive
counterpart of $\game{4}(A)$.  \tsnote{This statement is unjustified.
(See my comments below.) Actually it's meaningless, because games are
not not adaptive or non-adaptive.  Adversaries are.}

\tsnote{You need to just justify these next lines better. For example,
why is the event $\neg \bad$ independent of the event $\game{3}(A)=1$?}
\begin{align}
\nonumber \Prob{\game{4}(A)=1} &= \Prob{\game{3}(A)=1 \wedge \neg\bad}\\ 
\nonumber & = \Prob{\game{3}(A)=1}\Prob{\game{3}(A):\,\neg\bad}\\
& = \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:3a}\\
\Prob{\game{5}(A)=1} &= \Prob{\game{4}(A)=1}\label{eq:3b}
\end{align}

\tsnote{Why is $B_2$
  sampling a random function?  This ruins the tightness of security
  bound w.r.t.\ resources.  Please have~$B_2$ carry out lazy sampling
  of~$\rho_2$.  Also, please use the macro for Func.}

\tsnote{This proof jumps around too much.  The games should be
  addressed in order, as much as possible.}  
The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries, and~$D$ is one such adversary simulating $\game{5}(A)$ as closely as possible, whereas $D'$ mimics $D$ for $r=1$. $D'$ outputs a FP as in a classic Bloom filter and its FP-error is upperbounded by $[(1-e^{-kn/m})^k +O(1/n)]$ \cite{KirschMitzenmacher}.  %\acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.  It suffices to say this.}
\noindent
From \Cref{fig:AGame3}, it is evident that \tsnote{Where is the
  set~$S$ in $D$ and $D'$?  Make sure to give it to~$A$.  Why is this
  extra set~$\mathcal{Y}$ needed?  What is the point of~$D'$? }
\begin{align}
\Prob{\game{5}(A)=1} &= \Prob{D \, \mbox{outputs $r$ FP} \,}\label{eq:4a}\\
\nonumber \Prob{D \, \mbox{outputs r FP} \,} &=  \Big[\Prob{D' \, \mbox{outputs FP} \,}\Big]^r\\
& \leq \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r \label{eq:4b}
\end{align}
\tsnote{How does the second line follow?  You're claiming independence
  somehow, but you haven't justified it.}
\noindent
From \Cref{eq:4a,eq:4b}
\begin{equation}
\Prob{\game{5}(A)=1} \leq [(1-e^{-kn/m})^k + O(1/n)]^r \label{eq:4}
\end{equation}

\noindent
Using \ref{eq:4} in \ref{eq:3c}:
\begin{align}
\nonumber \Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}}  &\leq [(1-e^{-kn/m})^k +O(1/n)]^r\\
 \Prob{\game{2}(A)=1}  & \leq \dbinom{q}{r}[(1-e^{-kn/m})^k +O(1/n)]^r\label{eq:5}
\end{align}

\fixme{These adversaries are incorrect.  They are FP adversaries, so
  they get~$S$ as input.  They also do not sample random functions;
  use lazy sampling (a la game $\game{3}(A)$.  Please clean things up.)}
\noindent
%\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
%\begin{figure}
%\centering
%\fpage{0.8}
%{
%\hpagess{0.5}{0.4}{
%\underline{$\game{5}(A)$}\\
%$c \gets 0$\\
%$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
%$\calY \gets \emptyset$\\
%$S \getsr \distr{\univ}{n}$\\
%$M \getsr \Rep^{\HashOracle}(\calS)$\\
%$\calZ \getsr A^{\QryOracle}(\calS)$\\
%if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
%\nudge Ret 0\\
%if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
%\nudge Ret 1\\
%Ret 0
%}
%
%{
%\oracle{$\QryOracle(x)$}\\
%$c \gets c+1$\\
%if $c \in \mathcal{I}$ then\\
%\nudge $\calY \gets \calY \cup {x}$\\
%\nudge Ret 1\\
%else\\
%\nudge Ret 0 \\\\
%
%\oracle{$\HashOracle(x)$}\\
%$a,b \getsr [m]$\\
%for $i = 1$ to~$k$\\
%\nudge $v_i = a+i \cdot b \bmod m$\\
%Ret $\left(v_1,\ldots,v_k\right)$
%}
%}
%\caption{\Cref{thm1}:$\game{5}(A)$ in game playing argument}\label{fig:game5}
%\end{figure}

>>>>

%\acnote{I am moving comments to end of the proof in tex file and commenting them as the labels are getting mangled}
\heading{Linear-PRF construction. }
Here we consider a hash-based filter that was attacked by Neidermayer et al. in~\cite{xxx}.  Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be defined as follows.  Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.  Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.  The $\Hash$ algorithm samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.  The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones. $B_{\mathrm{lin}}$ is in fact one instantiation of a set-multiplicity data structure. It must be noted that $B_{\mathrm{lin}}$ admits errors in form of false-positives only. So, error rate of $B_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate. The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $B_\mathrm{lin}$ is correct against adaptive error-finding adversaries. Henceforth, we refer errors and error-rate in $B_{\mathrm{lin}}$ as false-positives and false-positive(FP) rate, respectively.

\begin{theorem}\label{thm1}
Fix $k,m,n,r>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
For any adversary~$A$ that makes a total of~$q$ queries to its oracle
and has time-complexity~$O(t)$,
there exist adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
\end{theorem}
Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, non-adaptive) FP-probability for~$B_\mathrm{lin}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as 
$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
trying to find a single FP in each of~$r$ independent``rounds'', each round
consisting of~$q$ attempts.

\begin{proof}[\Cref{thm1}]
The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpCorrect{B_\mathrm{lin},\distr{\calS}{},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,

\begin{equation}
\AdvCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
\end{equation}

@@

\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(S, \pubaux)$\\
When $A$ asks $\TestOracle(q)$:\\
\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
\nudge if $a \neq q(S)$ then \\
\nudge \nudge $\err \gets \err +1$\\
Return~$(a,\err )$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1\\\\
%
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
Run~$A(S, \pubaux)$\\
When $A$ asks $\TestOracle(q)$:\\
\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
\nudge if $a \neq q(S)$ then \\
\nudge \nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\
When $A$ halts: \\
\nudge if $\err  < r$ then Return 0\\
\nudge Return 1\\\\
\oracle{$\HashOracle(x)$}\\
$a \getsr [m]$\\
if $T[x] \neq \undefined$\\
\nudge $a \gets T[x]$\\
$T[x] \gets a$\\
Ret  $\calO(x) + i\cdot a$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

@@

Recall that adversary~$A$ wins $\ExpCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{}$ by finding~$r$ false positives. We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive.  We can also assume that every point in $\calZ$ has already been queried to $\QryOracle$.  This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. 
%
Under these assumptions, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.  We give this~$D$ in \Cref{fig:D}. Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be the false positives; it simulates the~$\QryOracle$ by returning 1 on the guessed queries, and 0 otherwise; and it halts by outputting the set of guessed queries.  Thus we have
$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{B}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}$.

Note that $\tilde{B}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).  Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a non-adaptive adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.  For $r>1$, we observe that~$A$'s queries are distinct and not elements of the original set~$S$, since we assume no pointless queries. Hence, so are the points $x_1,x_2,\ldots,x_r$ returned by~$D$.  Let $\calF_i$ be the event that~$x_i$ is a false positive.  Since $\game{4}$ (equivalently $\tilde{B}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent. 
\[
\Prob{\ExpCorrect{\tilde{B}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
\]

To summarize, we have 
\[
\AdvCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
\]
which is the bound claimed in the theorem statement. \hfill \qed

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\err \gets\err +1$\\
Return~$(a,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
$c\gets 0$, $\bad \gets \false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$S \getsr \distr{\calS}{}$\\
$\err \gets 0$\\
$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\\\
%
\oracle{$\TestOracle(q)$}\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
if $c \in \mathcal{I}$ and $a \neq q(S)$ then \\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $a \neq q(S)$ then \\
\nudge $\bad \gets \true$\\
\nudge $\err \gets\err +1$\\
Return~$(v,\err )$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

@@

%\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\begin{figure}
\centering
\fpage{0.35}
{
$\adversaryv{D(S)}$\\[4pt]
$c \gets 0$, $\calX \gets \emptyset$\\
$\err \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
Run $A(S)$\\
When $A$ asks $\QryOracle(x)$:\\
\nudge $c \gets c+1$\\
\nudge $r \gets 0$\\
\nudge if $c \in \mathcal{I}$\\
\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
\nudge \nudge $r \gets 1$\\
\nudge \nudge $\err \gets \err + 1$\\
\nudge Ret $(r,\err )$\\
When $A$ halts:\\
\nudge Ret $\calX$
}
\caption{\Cref{thm1}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
\end{figure}

\end{proof}
